Fusing Filters with Integer Linear Programming

### 2014-05-09 2014betterfusionforfilters/section/05-Benchmarks.tex
benchmarks. allegedly

\subsection{Quickselect}
We can't quite do @quickselect@, sadly; it requires @head@.
\begin{code}
select :: Vec a -> Int -> a
select xs k
 | length xs > 0
 = let p    = head xs 
       xslt = filter  (<p) xs
       xsge = filter (>=p) xs
   in  if     length xslt > k
       then   select xsge (k - length xslt)
       else   select xslt  k
 | length xs == 1
 = head xs
 | length xs == 0
 = error "Empty array!"

median :: Vec a -> a
median xs
 = select xs (length xs `div` 2)
\end{code}

>>>>

\begin{tabular}{lrrr}
                &   Unfused         & Stream fusion   & \textbf{ ILP               }\\
Normalise2      &   14.0s           & 12.3s           & \textbf{ 11.4s             }\\
Closest pairs   &   25.6s           & 25.1s           & \textbf{ 22.4s             }\\
QuadTree        &   x               & x               & \textbf{ x                 }\\
\end{tabular}

Notes:
\begin{itemize}
\item
Normalise2 tested with around 1gb input data. This should be small enough that all intermediates fit in memory, but large enough not to fit in cache.
\item
ClosestPoints only tested with 80mb data.
\item
ILP solutions were created by hand-fusing based on the clustering of the implementation. In the future, this will be integrated to use data flow fusion.
\item
Benchmark programs are available at \url{https://github.com/amosr/clustering/tree/master/benches/code}
\end{itemize}
